\textit{Complex Variables and Elliptic Equations} \LaTeX\ guide for authors (Style 2 + NLM reference style)

### 2016-12-22 cvee_paper_gerasimovd.tex
No need for index

{\abstractfont\centerline{\bfseries Index to information contained in this guide}\vspace{12pt}
\hbox to \textwidth{\hsize\textwidth\vbox{\hsize17pc
\hspace*{-12pt} {1.}    Introduction\\
\hspace*{7pt} {1.1.}  The \textit{gCOV} document class\\
\hspace*{7pt} {1.2.}  Submission of \LaTeX\ articles\\
\hspace*{24pt}        to the journal\\
{2.}    Using the \textit{gCOV} class file\\
{3.}    Additional features\\
\hspace*{10pt}{3.1.}  Title, authors' names, abstract\\
\hspace*{24pt}        and keywords\\
\hspace*{10pt}{3.2.}  Additional footnotes to the\\
\hspace*{24pt}        title or authors' names\\
\hspace*{10pt}{3.3.}  Lists\\
{4.}    Some guidelines for using\\
\hspace*{6pt}        standard features\\
\hspace*{10pt}{4.1.}  Sections\\
\hspace*{10pt}{4.2.}  Illustrations (figures)\\
\hspace*{10pt}{4.3.}  Tables\\
\hspace*{10pt}{4.4.}  Landscape pages\\
\hspace*{10pt}{4.5.}   Theorem-like environments\\
\noindent \hspace*{7pt} {4.6.}   Typesetting mathematics\\
\hspace*{24pt} {4.6.1.}  Displayed mathematics\\
\hspace*{24pt} {4.6.2.}  Bold math italic symbols\\
\hspace*{24pt} {4.6.3.}  Bold Greek\\
\hspace*{24pt} {4.6.4.}  Upright Greek characters \\
\hspace*{47pt}            and the upright partial \\
\hspace*{47pt}            derivative sign }
\hspace{-24pt}\vbox{\noindent\hsize17pc
\hspace*{7pt} {4.7.}   Acknowledgements \\
\hspace*{7pt} {4.8.}   Disclosure \\
\hspace*{7pt} {4.9.}   Funding \\
\hspace*{7pt} {4.10.}   Notes \\
\hspace*{7pt} {4.11.}   Supplemental material \\
\hspace*{7pt} {4.12.}   References \\
\hspace*{24pt} {4.12.1.}  References cited in the \\
\hspace*{52pt}            text\\
\hspace*{24pt} {4.12.2.}  The list of references\\
\hspace*{7pt} {4.13.}   Appendices \\
{5.}    Example of a section heading \\*
\hspace*{6pt}   including {\fontencoding{T1}\scshape{small caps}}, \textit{italic}, \\
\hspace*{6pt}   and bold Greek such as ${\bm\kappa}$ \\
{6.}    \textit{gCOV} journal style \\
\hspace*{10pt}{6.1.}   Hyphens, en rules, em rules \\ \hspace*{27pt}and minus signs\\
\hspace*{10pt}{6.2.}   References \\
\hspace*{10pt}{6.3.}   Maths fonts\\
{7.}    Troubleshooting\\
{8.}    Fixes for coding problems\\
{9.}    Obtaining the \texttt{gCOV2e} class file\\
\hspace*{10pt}{9.1}  Via the Taylor \& Francis \\
\hspace*{24pt}       website\\
\hspace*{10pt}{9.2}  Via e-mail\\}}}

@@

First, we check that $a > b$:
\begin{align*}
   R + \frac{(C + 1)^2}{R} - 2 (C + 1)
   &= \frac{R^2 + C^2 + 2C + 1 - 2 RC - 2 R}{R}
\\ &= \frac{(C - R)^2 + 2(C - R) + 1}{R}
\\ &= \frac{(C - R + 1)^2 }{R}
\\ &> 0 && \text{,strictly greater since $C > R$} 
\end{align*}

Next, we compute en estimate for $\sqrt{a^2 - b^2}$:
\begin{align*}
a^2 - b^2
& =  (R + \frac{(C + 1)^2}{R})^2 - (2 (C + 1))^2\\
& =  R^2 + \frac{(C+1)^4}{R^2} + 2 (C+1)^2 - 4 (C + 1)^2 \\
& =  \left( \frac{(C + 1)^2}{R} - R \right)^2 \\
& =  \left( \frac{(C + 1)^2 - R^2}{R}\right)^2 \\
& =  \left( \frac{(C + 1 - R) (C + 1 + R)}{R}\right)^2 && \text{,since $C > R > 0$} \\
&\ge \left( \frac{(1) (R + R)}{R}\right)^2  \\
&\ge 4
\end{align*}

@@

Given these facts, we can build a simple lower bound for $s(x + \mathrm{i} y)$:
\begin{align*}
l(x + \mathrm{i} y)
   &= \left|\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}\right|
\\ &= \left|\frac{\tanh y - V}{\tanh y + V}\right| && \text{(since $\cosh y > 0$)}
\end{align*}

@@

First, note that on $Z \le y \le R + C$ the function $\frac{1}{\sqrt{R - C + y}}$ has no singularities and we can estimate integral \ref{eq:int_f} as:
\begin{equation}\label{eq:int_f_up}
\begin{aligned}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}} 
\end{aligned}
\end{equation}

@@

Let's estimate \ref{eq:int_f_up}, replacing functions under the integral sign by their extreme value at interval's ends:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
\\ =   & \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}} \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \int \ln^2 f(y) 
\end{align*}

@@

\paragraph{$Z + \frac{1}{R} \le y < C$}
Again, by picking extreme values for the parts of integrands, we can estimate \ref{eq:int_f_up} as:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(Z + \frac{1}{R}) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}}
\\  =  & \ln^2 f(Z + \frac{1}{R})  \frac{R}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{R^2 - C^2 + 2 (C + 1) y + 1}
\end{align*}

@@

Again, estimating \ref{eq:int_f_up} from above:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
\end{align*}

>>>>

@@

First, we check that $a > b$:
\begin{align*}
   R + \frac{(C + 1)^2}{R} - 2 (C + 1)
   &= \frac{R^2 + C^2 + 2C + 1 - 2 RC - 2 R}{R}
\\ &= \frac{(C - R)^2 + 2(C - R) + 1}{R}
\\ &= \frac{(C - R + 1)^2 }{R}
\\ &> 0 && \text{,\ strictly greater since $C > R$} 
\end{align*}

Next, we compute en estimate for $\sqrt{a^2 - b^2}$:
\begin{align*}
a^2 - b^2
& =  (R + \frac{(C + 1)^2}{R})^2 - (2 (C + 1))^2\\
& =  R^2 + \frac{(C+1)^4}{R^2} + 2 (C+1)^2 - 4 (C + 1)^2 \\
& =  \left( \frac{(C + 1)^2}{R} - R \right)^2 \\
& =  \left( \frac{(C + 1)^2 - R^2}{R}\right)^2 \\
& =  \left( \frac{(C + 1 - R) (C + 1 + R)}{R}\right)^2 && \text{,\ since $C > R > 0$} \\
&\ge \left( \frac{(1) (R + R)}{R}\right)^2  \\
&\ge 4
\end{align*}

@@

Given these facts, we can build a simple lower bound for $s(x + \mathrm{i} y)$:
\begin{align*}
l(x + \mathrm{i} y)
   &= \left|\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}\right|
\\ &= \left|\frac{\tanh y - V}{\tanh y + V}\right| && \text{,\ since $\cosh y > 0$}
\end{align*}

@@

First, note that on $Z \le y \le R + C$ the function $\frac{1}{\sqrt{R - C + y}}$ has no singularities and we can estimate the integral (\ref{eq:int_f}) as:
\begin{equation}\label{eq:int_f_up}
\begin{aligned}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}} 
\end{aligned}
\end{equation}

@@

Let's estimate (\ref{eq:int_f_up}), replacing functions under the integral sign by their extreme value at interval's ends:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
\\ =   & \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}} \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \int \ln^2 f(y) 
\end{align*}

@@

\paragraph{$Z + \frac{1}{R} \le y < C$}
Again, by picking extreme values for the parts of integrands, we can estimate (\ref{eq:int_f_up}) as:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(Z + \frac{1}{R}) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}}
\\  =  & \ln^2 f(Z + \frac{1}{R})  \frac{R}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{R^2 - C^2 + 2 (C + 1) y + 1}
\end{align*}

@@

Again, estimating (\ref{eq:int_f_up}) from above:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
\end{align*}
